A-maze: Easier measurement of incremental processing

### 2021-04-19 Papers/UCI_2021/uci_2021.tex
start talk

\title{A-maze: Easier measurement of incremental processing}
\author{Veronica Boyce}
\date{3 June 2020}

@@

%

@@

			\includegraphics[width=.9\textwidth]{eye-tracker.jpeg}
			\pause
			\begin{itemize}
				\item Expensive
				\item Hard to analyse
			\end{itemize}
		\end{center}
	\end{column}\pause
	\begin{column}{.5\textwidth}
		\begin{center}
\textbf{\Large Self-paced reading}

@@

\begin{tikzpicture} %TODO on slide etc
\draw (-.5,-.5) rectangle (3.2,.5);
\onslide<4>{\node at (0,0) {The};}
\onslide<4>{\node at (1.7,0) {- - - - - - - - - - -};}
\onslide<5>{\node at (0,0) {- - - };}
\onslide<5>{\node at (.7,0) {cat};}
\onslide<5>{\node at (2,0) {- - - - - - - - };}
\onslide<6>{\node at (0.3,0) {- - - - - - };}
\onslide<6>{\node at (1.6,0) {drank};}
\onslide<6>{\node at (2.6,0) {- - - -};}
\onslide<7->{\node at (.9,0) {- - - - - - - - - - -};}
\onslide<7->{\node at (2.7,0) {milk.};}
\end{tikzpicture}
\end{center}
\onslide<8->{
			\begin{itemize}
	\item Lots of spillover
	\item Messy data 
\end{itemize}
}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{A third option: Maze}
\end{frame}
\begin{frame}{Maze Task}
\centering
\tikzset{
	font={\fontsize{14pt}{12}\selectfont}}
\begin{tikzpicture}
\onslide<1->{\node[draw] (a) at (-1,-.5) {e};}
\onslide<1->{\node[draw] (b) at (1,-.5) {i};}
\onslide<1-2>{\node  (c) at (-1,.5) {The};}
\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
\onslide<3-4>{\node  (d) at (1,.5) {dog};}
\onslide<5-6>{\node  (c) at (-1,.5) {revise};}
\onslide<5-6>{\node  (d) at (1,.5) {chased};}
\onslide<7-8>{\node  (c) at (-1,.5) {the};}
\onslide<7-8>{\node  (d) at (1,.5) {wish};}
\onslide<9-10>{\node  (c) at (-1,.5) {mitigate.};}
\onslide<9-10>{\node  (d) at (1,.5) {squirrel.};}
\onslide<2,8>{\node[draw, fill=pink!50] at (a) {e};}
\onslide<4,6,10>{\node[draw, fill=pink!50] at (b) {i};}
\end{tikzpicture}
\end{frame}

\begin{frame}{A third option: Maze}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{center}
		\textbf{\large G-maze}
		\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{gmaze.pdf}
		\end{center}
	\pause
	\end{column}
	\begin{column}{0.5\textwidth} 
		\begin{center}
		\textbf{\large L-maze}
			\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{lmaze.pdf}
		\end{center}
	\end{column}
\end{columns}

@@

\section{Experiment 1a}
\begin{frame}{Web Implementation}
Maze well suited to run on the web
\begin{itemize}
	\item Implement in Ibex
\end{itemize} 
\pause

@@

\end{small}
\includegraphics[width=\textwidth]{g_rel.pdf}
\end{frame}

@@

\end{small}
\includegraphics[width=\textwidth]{g_adv.pdf}
\end{frame}

\begin{frame}{Results}
\begin{small}	
\sethlcolor{green}The swimmer disappointed her coach\hl{,} and her mother \hl{tried} / \sethlcolor{pink}\hl{tried} to console her.
\end{small}
\includegraphics[width=\textwidth]{g_svnp.pdf}
\end{frame}

\begin{frame}{Interim Summary}
\textcolor{PineGreen}{\Large \textbf{Good news:} G-maze works well over the web (better than L-maze or SPR)}

\textcolor{Red}{\Large \textbf{Bad news:} I do not want to write G-maze materials.}

@@

@@

\begin{frame}
\centering
\includegraphics[clip, trim=3.25cm 5cm 2.5cm 2.5cm,width=.9\textwidth]{flow_2.pdf}
\end{frame}
\section{Experiment 1b}

\begin{frame}{Does A-maze work? }
\pause
Test it on materials from Witzel et al. (2012)
\medskip

\pause
Try with two pre-trained LSTM models (Gulordava 2018, Jozefowicz 2016)

@@

\begin{frame}{Does A-maze work?  Yes.} \pause
\includegraphics[width=1\textwidth]{a_all.pdf}
\end{frame}

\begin{frame}{Caveats}
A lot of mistakes on the second word of the sentence ("The \ul{dog} ...") \pause
\includegraphics{graph_errors2.pdf} \pause
Bad participants or bad distractors?

Either way, lots of data loss.
\end{frame}

@@

\section{Experiment 2}

\begin{frame}{Potential improvements}

{\large Option 1: Choose better distractors.} \pause
\begin{itemize}
	\item Tweak thresholds of distractor selection. \pause
	\item Could search for optimal thresholds. \pause
	\item Could manually check and fix distractors. 
\end{itemize}

@@

\begin{frame}{Potential improvements}

{\large Option 2: Be forgiving.} \pause
\begin{itemize}
	\item Just don't terminate on mistakes. \pause
	\item Instead have participant correct mistake and continue.
	\end{itemize}
\end{frame}

\begin{frame}{Maze with Error Correction}
\centering
\tikzset{
	font={\fontsize{14pt}{12}\selectfont}}
\begin{tikzpicture}
\onslide<1->{\node[draw] (a) at (-1,-.5) {e};}
\onslide<1->{\node[draw] (b) at (1,-.5) {i};}
\onslide<1-2>{\node  (c) at (-1,.5) {The};}
\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
\onslide<3-4>{\node  (d) at (1,.5) {dog};}
\onslide<5-8>{\node  (c) at (-1,.5) {revise};}
\onslide<5-8>{\node  (d) at (1,.5) {chased};}
\onslide<9-10>{\node  (c) at (-1,.5) {the};}
\onslide<9-10>{\node  (d) at (1,.5) {wish};}
\onslide<11-12>{\node  (c) at (-1,.5) {mitigate.};}
\onslide<11-12>{\node  (d) at (1,.5) {squirrel.};}
\onslide<2,6,10>{\node[draw, fill=pink!50] at (a) {e};}
\onslide<4,8,12>{\node[draw, fill=pink!50] at (b) {i};}
\onslide<7,8>{\node[text=red] at (0,-1.5) {\small Incorrect. Please try again.};}
\end{tikzpicture}
\end{frame}

@@

{\large The ``solution'' to our problems!} \pause

\begin{columns}
	\begin{column}{0.3\textwidth}
		\begin{center}
		\includegraphics[clip, trim=9cm 12.5cm 10cm 1cm,width=\textwidth]{maze_diagram.pdf}
		\end{center}

	\end{column} \pause 
	\begin{column}{0.7\textwidth} 
		\begin{center}
			\begin{itemize}
				\item Easily implemented as a toggle in Ibex \pause
				\item Have all the data \pause
				\item Identify bad participants v bad distractors 
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\medskip
\pause

Side effect: Can now run multi-sentence items!
\end{frame}

 %TODO: Needs work from here on!

\begin{frame}{Natural Stories}
Natural stories corpus (Futrell et al. 2017)
\begin{itemize}
	\item 10 stories, each about 1000 words
	\item Some unusual constructions, but read fluently
	\item 6 comprehension questions per story
\end{itemize}

@@

\begin{frame}{Experiment Plan}
Experiment questions:
\begin{itemize}
	\item Will people do this task?
	\item Can participants comprehend the stories?
\end{itemize}

@@

Checks on RT data
\begin{itemize}
	\item Check if RT is linear in surprisal (Smith \& Levy 2013)
	\item Check for known effects of word length, frequency
	\item Check for spillover effects
\end{itemize}

@@

\begin{frame}{Participant accuracy}
100 participants each read 1 story \pause
\begin{center}
\includegraphics[width=.8\textwidth]{error.pdf}
\end{center}
\end{frame}
\begin{frame}{Comprehension questions}
\begin{center} \pause
\includegraphics[width=.8\textwidth]{comp.pdf}
\end{center}
\end{frame}

\begin{frame}{Surprisal Effects}

Use 3 LMs to estimate surprisal: smoothed 5-gram, Gulordava RNN, Transformer-XL (Gulordava et al. 2018, Dai et al. 2019)
\pause

Fit GAMs on pre-error data.
\begin{itemize}
	\item Limit to single-token words.
	\item Fit to both current and past word surprisal.
\end{itemize}

@@

\begin{frame}{Surprisal Effects}
\includegraphics[width=.9\textwidth]{gam.pdf}	
\end{frame}
\begin{frame}{What about post-mistake data?}
Exclude data from mistakes or the two words after a mistake.

\includegraphics[width=.9\textwidth]{gam2.pdf}	
\end{frame}

\begin{frame}{Summary}
\begin{itemize}\pause
	\item People will read in the Maze task for 15-20 minutes \pause
	\item It's possible to comprehend during Maze \pause
	\item Distractors are generally good enough \pause
	\item Find expected RT patterns \pause
	\item Very little spillover
\end{itemize}
\end{frame}
\section{Conclusion}

\begin{frame}{Use A-maze!}
Easy to use! \pause
\begin{itemize}
	\item Runs on command line \pause
	\item Match distractors across minimal pair sentences \pause
	\item Customize surprisal thresholds, vocabulary lists \pause
	\item Can output pre-formatted for Ibex
\end{itemize}
\medskip
\end{frame}

\begin{frame}{Use A-maze!} \pause
Contribute to A-maze:
\begin{itemize}
	\item Written in Python 3 \pause
	\item Interface with other language models \pause
	\item Add more frequency sources \pause
	\item Extend to non-English languages
\end{itemize}

@@

\item Sample task: syntaxgym.org:666

@@

\begin{frame}{Matching distractors}
If unspecified: Match by position
\begin{itemize}
	\item The son of the lady who politely introduced \sethlcolor{green} \hl{herself}\sethlcolor{pink} / \hl{himself} was popular at the party.
\end{itemize}
Can specify labels for each word to pair (within item)
\begin{itemize}
	\item The cat who the dog scared hid in a box.\\pre-1 pre-2 who art noun verb main-verb post-1 post-2 post-3
\item The dog who scared the cat sniffed around the couch.\\ pre-1 pre-2 who verb art noun main-verb post-1 post-2 post-3
\end{itemize}
\end{frame}
%back pocket on more on model results??
%do we even need back pockets??

\begin{frame}{Post-mistake only}
Exclude data from mistakes or the two words after a mistake.

\includegraphics[]{gam3.pdf}	
\end{frame}

\begin{frame}{Regression coefficients}
\begin{tiny}
\begin{tabular}{l|rlr|rlr|rlr}
	\hline
	&\multicolumn{3}{c|}{5-gram}&\multicolumn{3}{c|}{GRNN}&\multicolumn{3}{c}{TXL}\\
	& Est & CI & $p$ & Est & CI & $p$ &Est & CI & $p$ \\ 
	\hline
	Intercept & 865.3 & [829.9, 902.9] & 0.00 & 871.1 & [837.9, 905.3] & 0.00 & 870.8 & [832.5, 907.8] & 0.00 \\ 
	Surprisal & 11.7 & [9.3, 14.1] & 0.00 & 23.7 & [21, 26.5] & 0.00 & 18.5 & [16.1, 21.1] & 0.00 \\ 
	Frequency & -2.9 & [-6.3, 0.5] & 0.10 & 2.9 & [-0.2, 6] & 0.06 & 0.4 & [-2.7, 3.5] & 0.79 \\ 
	Length & 20.5 & [15.4, 25.6] & 0.00 & 18.5 & [13.3, 23.7] & 0.00 & 21.4 & [16.2, 26.6] & 0.00 \\ 
	Surprisal:Length & -2.0 & [-3, -1] & 0.00 & -1.8 & [-2.7, -0.9] & 0.00 & -1.4 & [-2.2, -0.6] & 0.00 \\
	Freq:Length & -1.0 & [-2.5, 0.4] & 0.16 & -0.1 & [-1.2, 1] & 0.82 & 0.2 & [-0.9, 1.2] & 0.76 \\ 
	\hline
	Past Surprisal & 1.6 & [-0.5, 3.6] & 0.14 & 2.7 & [0.8, 4.5] & 0.00 & 0.8 & [-0.9, 2.5] & 0.40 \\ 
	Past Freq & 2.6 & [-0.1, 5.4] & 0.06 & 1.9 & [-0.2, 4.2] & 0.08 & 1.2 & [-1.1, 3.6] & 0.30 \\ 
	Past Length & -4.8 & [-9, -0.1] & 0.04 & -6.6 & [-10.9, -2.1] & 0.00 & -5.2 & [-9.3, -0.7] & 0.03 \\ 
	Past Surp:Length & -0.2 & [-1.2, 0.8] & 0.72 & -0.9 & [-1.7, -0.2] & 0.01 & -0.6 & [-1.3, 0.2] & 0.13 \\ 
	Past Freq:Length & -1.0 & [-2.3, 0.3] & 0.15 & -1.8 & [-2.9, -0.8] & 0.00 & -1.5 & [-2.6, -0.5] & 0.01 \\

	\hline
\end{tabular}
\end{tiny}
\end{frame}

\end{document}

>>>>

\DeclareRobustCommand{\greencheck}{%
	\tikz\fill[scale=0.6, color=ForestGreen]
	(0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;%
}
\title{A-maze: Easier measurement of incremental processing}
\author{Veronica Boyce}
\date{26 April 2021}

@@

\begin{frame}{Road map} %Acknowledge collaborators 
	%TODO: find a picture of Richard!!
	Methods talk 
	- briefly summarize RT methods, introduce Maze task
	- talk through study 1 (w/ Roger and Richard) where we created and tested this variant method
	- talk through study 2 where I tweaked the method and did another study
	- have a little historical revisionism -- there were some boring implementational tweaks, so what I'll present is a little different that what was used in the first study
	\begin{tikzpicture}[remember picture,overlay]
	\node[xshift=-1.8cm,yshift=-1cm] at (current page.east) {\includegraphics[clip, trim=.1cm 0cm .2cm 0cm,width=.2\textwidth]{../Images/roger.jpg}};
	\end{tikzpicture}

	\begin{tikzpicture}[remember picture,overlay]
	\node[xshift=2.5cm,yshift=-1.5cm] at (current page.north west) {\includegraphics[width=.3\textwidth]{../Images/cpl_header.png}};
	\end{tikzpicture}

\end{frame}
%

@@

			\includegraphics[width=.9\textwidth]{../Images/eye-tracker.jpeg}
			\pause
			\begin{itemize}
				\item Expensive
				\item Hard to analyse
			\end{itemize}
		\end{center}
	\end{column}\pause
	\begin{column}{.5\textwidth}
		\begin{center}
\textbf{\Large Self-paced reading}

@@

\begin{tikzpicture} 
\draw (-.5,-.5) rectangle (3.2,.5);
\onslide<4>{\node at (0,0) {The};}
\onslide<4>{\node at (1.7,0) {- - - - - - - - - - -};}
\onslide<5>{\node at (0,0) {- - - };}
\onslide<5>{\node at (.7,0) {cat};}
\onslide<5>{\node at (2,0) {- - - - - - - - };}
\onslide<6>{\node at (0.3,0) {- - - - - - };}
\onslide<6>{\node at (1.6,0) {drank};}
\onslide<6>{\node at (2.6,0) {- - - -};}
\onslide<7->{\node at (.9,0) {- - - - - - - - - - -};}
\onslide<7->{\node at (2.7,0) {milk.};}
\end{tikzpicture}
\end{center}
\onslide<8->{
			\begin{itemize}
	\item Lots of spillover
	\item Messy data 
\end{itemize}
}
\end{column}
\end{columns}
	\bigskip
\onslide<8->{Different methods have different trade-offs}
\end{frame}

\begin{frame}[c]{An alternative: Maze}

	\centering

	\tikzset{
		font={\fontsize{14pt}{12}\selectfont}}
	\begin{tikzpicture}
	\onslide<1-2>{\node  (c) at (-1,.5) {The};}
	\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
	\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
	\onslide<3-4>{\node  (d) at (1,.5) {dog};}
	\onslide<5-6>{\node  (c) at (-1,.5) {revise};}
	\onslide<5-6>{\node  (d) at (1,.5) {chased};}
	\onslide<7-8>{\node  (c) at (-1,.5) {the};}
	\onslide<7-8>{\node  (d) at (1,.5) {wish};}
	\onslide<9-10>{\node  (c) at (-1,.5) {mitigate.};}
	\onslide<9-10>{\node  (d) at (1,.5) {squirrel.};}
	\onslide<2,8>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,align=center] at (c) {};}
	\onslide<4,6,10>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,
		align=center] at (d) {};}
	\end{tikzpicture}
\end{frame}

\begin{frame}{A third option: Maze}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{center}
		\textbf{\large G-maze}
		\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{../Images/gmaze.pdf}
		\end{center}
	\pause
	\end{column}
	\begin{column}{0.5\textwidth} 
		\begin{center}
		\textbf{\large L-maze}
			\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{../Images/lmaze.pdf}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Maze Made Easy}

	Can we use Maze instead of web SPR?\pause

	Needs some tweaks:\pause
	\begin{itemize}
		\item Run on web \pause
		\item Easily generate distractors \pause
		\item Work for multi-sentence items
	\end{itemize}

\section{Experiment 1a}
\begin{frame}{Run on web}

	\pause
	Wrote an Ibex module \pause

	\begin{center}\includegraphics[width=.7\textwidth]{../Images/screenshot.png} \end{center}\pause

@@

\end{small}
\includegraphics[width=\textwidth]{../Images/g_rel.pdf}
\end{frame}

@@

\end{small}
\includegraphics[width=\textwidth]{../Images/g_adv.pdf}
\end{frame}

\begin{frame}{Results}
\begin{small}	
\sethlcolor{green}The swimmer disappointed her coach\hl{,} and her mother \hl{tried} / \sethlcolor{pink}\hl{tried} to console her.
\end{small}
\includegraphics[width=\textwidth]{../Images/g_svnp.pdf}
\end{frame}

\begin{frame}{Maze Made Easy}

	Can we use Maze instead of web SPR?

	Needs some tweaks:
	\begin{itemize}
		\item Run on web \greencheck
		\item Easily generate distractors
		\item Work for multi-sentence items 
	\end{itemize}

@@

\begin{frame}{Generating distractors}
	\pause
	Goal: Find a word that can't continue a partial sentence
	\begin{itemize}
		\item Ex.  \textit{The dog chased} \pause
		\item Tedious (and hard!) to do by hand
	\end{itemize} \pause

	What makes something an unacceptable continuation? \pause
	\begin{itemize}
		\item Ungrammatical \pause
		\item ...or otherwise really unlikely \pause 
		\item $\approx$ high surprisal 
	\end{itemize} \pause

	Can we use Neural Language Models?
\end{frame}

@@

\begin{frame}
	\centering
	\includegraphics[clip, trim=3.25cm 5cm 2.5cm 2.5cm,width=.9\textwidth]{../Images/flow_2.pdf}
\end{frame}

\section{Experiment 1b}

\begin{frame}{Does it work?} 
	%\vskip -2em
	\small
	From ``Maze Made Easy'' (Boyce et al 2020)
	\medskip

	\centering

	\includegraphics[width=\textwidth]{../Images/spr_g_amaze.pdf}

	{\footnotesize Error bars: 95\% CI}

@@

\begin{frame}{Does it work?} 
	\pause
	%\vskip -2em
	{\large Yes, at least well enough.} \pause
	\begin{itemize}
		\item Sometimes generates plausible distractors. \pause
		\item Sloggett et al 2020 also found A-maze results comparable with G-maze
	\end{itemize} 
\end{frame}

\section{Error-correction A-Maze}

\begin{frame}{Maze Made Easy}

	Can we use Maze instead of web SPR?

	Needs some tweaks:
	\begin{itemize}
		\item Run on web \greencheck
		\item Easily generate distractors \greencheck
		\item Work for multi-sentence items 
	\end{itemize}

@@

\begin{frame}{Long items}

	Want to run multi-sentence items. \pause

	Problem: Errors terminate sentences. \pause
	\begin{itemize}
		\item Treat whole story as a unit: \pause Few participants make it to the end. \pause
		\item Treat each sentence as a unit: \pause Some participants miss key context. \pause

	\end{itemize}

	What if after an error, participants corrected errors and the sentence continued?

@@

\begin{frame}[c]{Maze with Error Correction}
	\centering
	\tikzset{
		font={\fontsize{14pt}{12}\selectfont}}

	\begin{tikzpicture}
	\onslide<1-2>{\node  (c) at (-1,.5) {The};}
	\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
	\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
	\onslide<3-4>{\node  (d) at (1,.5) {dog};}
	\onslide<5-8>{\node  (c) at (-1,.5) {revise};}
	\onslide<5-8>{\node  (d) at (1,.5) {chased};}
	\onslide<9-10>{\node  (c) at (-1,.5) {the};}
	\onslide<9-10>{\node  (d) at (1,.5) {wish};}
	\onslide<11-12>{\node  (c) at (-1,.5) {mitigate.};}
	\onslide<11-12>{\node  (d) at (1,.5) {squirrel.};}
	\onslide<2,6,10>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,align=center] at (c) {};}
	\onslide<4,8,12>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,
		align=center] at (d) {};}
	\onslide<7,8>{\node[text=red] at (0,-1.5) {\small Incorrect. Please try again.};}
	\end{tikzpicture}

@@

	Incidentally, also ``solves'' problem of bad distractors!

	\begin{columns}
		\begin{column}{0.4\textwidth}
			\begin{center}
				\includegraphics[clip, trim=9cm 12.5cm 10cm 1cm,width=\textwidth]{../Images/maze_diagram.pdf}
			\end{center}

		\end{column} \pause 
		\begin{column}{0.6\textwidth} 
			\begin{center}
				\begin{itemize}
					\item Can be toggled in Ibex Maze \pause
					\item Long materials feasible \pause
					\item Have all the data \pause
					\item Compensates for bad distractors
				\end{itemize}
			\end{center}
		\end{column}
	\end{columns}
\end{frame}
%
\begin{frame}{Maze Made Easy}

	Can we use Maze instead of web SPR?

	Needs some tweaks:
	\begin{itemize}
		\item Run on web \greencheck
		\item Easily generate distractors \greencheck
		\item Work for multi-sentence items \greencheck ? 
	\end{itemize}

\section{Experiment 2}
\begin{frame}{}
	Various open questions to address \pause
	\begin{itemize}
		\item Will people read long texts in Maze? \pause
		\item Will they comprehend what they read? \pause
		\item Does error correction Maze work? \pause
		\item Do we get predictability effects? 
	\end{itemize}
\end{frame}

\begin{frame}{Natural Stories}
	Natural stories corpus (Futrell et al. 2017) \pause
	\begin{itemize}
		\item 10 stories, each about 1000 words \pause
		%	\item Some unusual constructions, but read fluently \pause
		\item 6 comprehension questions per story
	\end{itemize}

@@

\begin{frame}{Participant accuracy}
100 participants each read 1 story \pause
\begin{center}
\includegraphics[width=.8\textwidth]{../Images/error.pdf}
\end{center}
\end{frame}
\begin{frame}{Comprehension questions}
\begin{center} \pause
\includegraphics[width=.8\textwidth]{../Images/comp.pdf}
\end{center}
\end{frame}

\begin{frame}{Surprisal Effects}
	\large{Is RT linear in terms of surprisal?}\pause
	\medskip

	Estimate surprisal from 3 models:
	\begin{itemize}
		\item smoothed 5-gram
		\item LSTM-RNN (Gulordava et al. 2018)
		\item Transformer-XL (Dai et al. 2019)
	\end{itemize}

@@

	Fit GAMs
	\begin{itemize}
		%\item Limit to single-token words
		\item Fit to both current and past word surprisal
		\item Include frequency, length as predictors
	\end{itemize}

@@

\begin{frame}{Surprisal Effects}
	\includegraphics[width=.9\textwidth]{../Images/amaze_gam.pdf}	
\end{frame}

\begin{frame}{SPR comparison}

	\includegraphics[width=\textwidth]{../Images/spr_gam.pdf}

@@

\begin{frame}{Surprisal Effects}
	\vskip -2em
	Linear Models \\ 
	\pause

	\begin{small}
		\begin{tabular}{l|r|r|r}
			\hline
			&5-gram & GRNN & TXL\\
			\hline
			Intercept & \textbf{865.3} & \textbf{871.1} & \textbf{870.8} \\ 
			Surprisal & \textbf{11.7}  & \textbf{23.7} & \textbf{18.5}  \\ 
			Frequency & -2.9  & 2.9  & 0.4  \\ 
			Length & \textbf{20.5} & \textbf{18.5}  & \textbf{21.4} \\ 
			Surprisal:Length & \textbf{-2.0}  & \textbf{-1.8}  & \textbf{-1.4} \\
			Freq:Length & -1.0  & -0.1 & 0.2  \\ 
			\hline
			Past Surprisal & 1.6  & \textbf{2.7} & 0.8 \\ 
			Past Freq & 2.6  & 1.9  & 1.2  \\ 
			Past Length & \textbf{-4.8}  & \textbf{-6.6 }&\textbf{ -5.2} \\ 
			Past Surp:Length & -0.2 & \textbf{-0.9} & -0.6  \\ 
			Past Freq:Length & -1.0  & \textbf{-1.8 }&   \textbf{-1.5}  \\ 
			\hline
		\end{tabular}

		Surprisal in bits, Length in characters, \\
		Frequency in $log_2$ occurrences/billion words
	\end{small}

\end{frame}
\begin{frame}{Surprisal Effects}
	Takeaways: \pause
	\begin{itemize}
		\item Minimal frequency effects (consistent with Shain 2019) \pause
		\item Large effects of Length, Surprisal \pause
		\item Very little spillover \pause
	\end{itemize}
	%	
	Model comparison: GRNN is best, but TXL complementary
\end{frame}

\begin{frame}{Summary}
	\begin{itemize}\pause
		\item People will read in the Maze task for 15-20 minutes \pause
		\item It's possible to comprehend during Maze \pause
		\item Distractors are generally good enough \pause
		\item Find expected RT patterns \pause
		\item Very little spillover
	\end{itemize}
\end{frame}

\section{Conclusion}

\begin{frame}{Consider A-maze!}
Easy to use! \pause
\begin{itemize}
	\item Runs on command line \pause
	\item Match distractors across minimal pair sentences \pause
	\item Customize surprisal thresholds, vocabulary lists \pause
	\item Can output pre-formatted for Ibex
\end{itemize}
\medskip
\end{frame}

\begin{frame}{Consider A-maze!} \pause
Adapt A-maze to your projects:
\begin{itemize}
	\item Written in Python 3 
	\item Interface with other language models 
	\item Add more frequency sources 
	\item Extend to non-English languages
\end{itemize}

@@

@@

\begin{frame}{Matching distractors}
If unspecified: Match by position
\begin{itemize}
	\item The son of the lady who politely introduced \sethlcolor{green} \hl{herself}\sethlcolor{pink} / \hl{himself} was popular at the party.
\end{itemize}
Can specify labels for each word to pair (within item)
\begin{itemize}
	\item The cat who the dog scared hid in a box.\\pre-1 pre-2 who art noun verb main-verb post-1 post-2 post-3
\item The dog who scared the cat sniffed around the couch.\\ pre-1 pre-2 who verb art noun main-verb post-1 post-2 post-3
\end{itemize}
\end{frame}

\begin{frame}{Regression coefficients}
\begin{tiny}
\begin{tabular}{l|rlr|rlr|rlr}
	\hline
	&\multicolumn{3}{c|}{5-gram}&\multicolumn{3}{c|}{GRNN}&\multicolumn{3}{c}{TXL}\\
	& Est & CI & $p$ & Est & CI & $p$ &Est & CI & $p$ \\ 
	\hline
	Intercept & 865.3 & [829.9, 902.9] & 0.00 & 871.1 & [837.9, 905.3] & 0.00 & 870.8 & [832.5, 907.8] & 0.00 \\ 
	Surprisal & 11.7 & [9.3, 14.1] & 0.00 & 23.7 & [21, 26.5] & 0.00 & 18.5 & [16.1, 21.1] & 0.00 \\ 
	Frequency & -2.9 & [-6.3, 0.5] & 0.10 & 2.9 & [-0.2, 6] & 0.06 & 0.4 & [-2.7, 3.5] & 0.79 \\ 
	Length & 20.5 & [15.4, 25.6] & 0.00 & 18.5 & [13.3, 23.7] & 0.00 & 21.4 & [16.2, 26.6] & 0.00 \\ 
	Surprisal:Length & -2.0 & [-3, -1] & 0.00 & -1.8 & [-2.7, -0.9] & 0.00 & -1.4 & [-2.2, -0.6] & 0.00 \\
	Freq:Length & -1.0 & [-2.5, 0.4] & 0.16 & -0.1 & [-1.2, 1] & 0.82 & 0.2 & [-0.9, 1.2] & 0.76 \\ 
	\hline
	Past Surprisal & 1.6 & [-0.5, 3.6] & 0.14 & 2.7 & [0.8, 4.5] & 0.00 & 0.8 & [-0.9, 2.5] & 0.40 \\ 
	Past Freq & 2.6 & [-0.1, 5.4] & 0.06 & 1.9 & [-0.2, 4.2] & 0.08 & 1.2 & [-1.1, 3.6] & 0.30 \\ 
	Past Length & -4.8 & [-9, -0.1] & 0.04 & -6.6 & [-10.9, -2.1] & 0.00 & -5.2 & [-9.3, -0.7] & 0.03 \\ 
	Past Surp:Length & -0.2 & [-1.2, 0.8] & 0.72 & -0.9 & [-1.7, -0.2] & 0.01 & -0.6 & [-1.3, 0.2] & 0.13 \\ 
	Past Freq:Length & -1.0 & [-2.3, 0.3] & 0.15 & -1.8 & [-2.9, -0.8] & 0.00 & -1.5 & [-2.6, -0.5] & 0.01 \\ 	
	\hline
\end{tabular}
\end{tiny}
\end{frame}

\begin{frame}{What about post-mistake data?}
	Exclude data from mistakes or the two words after a mistake.

	\includegraphics[width=.9\textwidth]{../Images/gam2.pdf}	
\end{frame}

\begin{frame}{Why such large effects?}
	\pause
	Bayesian Reader (Norris 2006): Look at words long enough to ID with some threshold of certainty \pause

	Possible mechanisms for difference: \pause
	\begin{itemize}
		\item Higher threshold \pause 
		\item Fewer available resources for processing \pause
		\item Presence of second word 
	\end{itemize}

\end{frame}
\end{document}
